Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-08-14 tex/sections/intro.tex
Improve readability
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Using succinct argument of knowledge systems makes an Argennon validator light enough to be implemented as a smart
contract. By deploying an Argennon validator on another turing complete smart contract platform, Argennon could use
more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet.

>>>>

Using succinct argument of knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. To reduce the execution fee, this validator
contract could be used for validating roll-ups of state transition.
